LAGOS lake depth

### 2020-11-27 manuscript/figures.Rmd
correct figure/table numbering and placement

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r depth_model_metrics, fig.cap = "Table 2: Model fit and predictive accuracy metrics (RMSE = root mean square error, R2 = coefficient of determination) for all combinations of true (in-lake slope, distance to the deepest point of the lake) and proxy (nearshore land slope, distance to lake center) metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
# see tables/02_model_metrics.Rmd
knitr::include_graphics("../tables/02_model_metrics.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{3}

>>>>

\captionsetup[figure]{name=Table}
\captionsetup[figure]{labelformat=empty}
```{r depth_model_metrics, fig.cap = "Table 1: Model fit and predictive accuracy metrics (RMSE = root mean square error, R2 = coefficient of determination) for all combinations of true (in-lake slope, distance to the deepest point of the lake) and proxy (nearshore land slope, distance to lake center) metrics.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
# see tables/02_model_metrics.Rmd
knitr::include_graphics("../tables/02_model_metrics.pdf")
```
\captionsetup[figure]{name=Figure}
\captionsetup[figure]{labelformat=default}
\setcounter{figure}{2}

### 2020-11-27 tables/02_model_metrics.Rmd
correct figure/table numbering and placement

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.path = "../figures/", fig.width = 5, fig.height = 6)
# setwd("tables")
```

@@

@@

dt_metrics[2,] <- paste0("**", dt_metrics[2,], "**") # highlight row from main text
clipr::write_clip(
  gsub("%\\*\\*", "\\\\%\\*\\*",
  gsub("_", "\\\\_",
  gsub("%\\\\", "\\\\%\\\\",
  sub("\\\\midrule", "\\\\hline",
  sub("\\\\bottomrule", "\\\\hline",
  sub("\\\\toprule", "\\\\hline",
      knitr::kable(dt_metrics, digits = 2, format = "latex",
     booktabs = TRUE, linesep = "", align = c("lllllc"), escape = FALSE)))))))
   )
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 5, fig.height = 6)
# setwd("tables")
```

@@

\clearpage

@@

# dt_metrics[2,] <- paste0("**", dt_metrics[2,], "**") # highlight row from main text
# clipr::write_clip(
#   gsub("%\\*\\*", "\\\\%\\*\\*",
#   gsub("_", "\\\\_",
#   gsub("%\\\\", "\\\\%\\\\",
#   sub("\\\\midrule", "\\\\hline",
#   sub("\\\\bottomrule", "\\\\hline",
#   sub("\\\\toprule", "\\\\hline",
#       knitr::kable(dt_metrics, digits = 2, format = "latex",
#      booktabs = TRUE, linesep = "", align = c("lllllc"), escape = FALSE)))))))
#    )
```
